Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-07-11 paper.tex
Replace Fig: moving fluid avg energy

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-moving_fluid-avg_eps_vs_cosA}
  \caption{Average energy $\langle\varepsilon\rangle=J/G$
    of neutrino fields for fluid moving in the $+z$ direction,
    with $A$ the angle between the neutrino momentum and the $+z$ direction.
    Test described in Sec.~\ref{ssec:test_doppler}}
  \label{fig:avg_eps_doppler}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-moving_fluid_avg_eps}
  \caption{Average energy $\langle\varepsilon\rangle=J/G$
    of neutrino fields for fluid moving in the $+z$ direction,
    with $A$ the angle between the neutrino momentum and the $+z$ direction.
    Test described in Sec.~\ref{ssec:test_doppler}.
    The points are computed from ray tracing spectra; the lines are the
    analytic formula.
  }
  \label{fig:avg_eps_doppler}
\end{figure}
